Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-04-13 talk/icooolps2011/paper.tex
fix a typo and an XXX

It is worth clarifying what is a ``constant'' in this context.  A variable of
the trace is said to be constant if its value is statically known by the
optimizer.

@@

Promoting integers, as in the examples above, is not used that often.
However, the internals of dynamic language interpreters often
have values that are variable but vary little in the context of parts of a user
program. An example would be the types of variables in a user function. Even
though in principle the argument to a Python function could be any Python type,
in practice the argument types tend not to vary often. Therefore it is possible to
promote the types. Section~\ref{sec:fastobjmodel} will present a complete example of how
this works.

\cfbolz{XXX explain how value specialization on the interpreter level can lead
to type specialization on the language level}

>>>>

It is worth clarifying what a ``constant'' is in this context.  A variable of
the trace is said to be constant if its value is statically known by the
optimizer.

@@

Promoting integers, as in the examples above, is not used that often.
However, the internals of dynamic language interpreters often
have values that are variable but vary little in the context of parts of a user
program. An example would be the types of variables in a user function, which
rarely change in a dynamic language in practice (even though they could). In the
interpreter, these user-level types are values. Thus promoting them will lead
to type-specialization on the level of the user program.
Section~\ref{sec:fastobjmodel} will present a complete example of how this
works.
